%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\usepackage{calc} % added

\newcommand{\resumeSubSubheadingLeft}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	\textbf{\Huge \scshape Henry Richter} \\ \vspace{1pt}
	\small +49 17657 660097 $|$
	\href{mailto:hr.richterhenry@gmail.com}{\underline{hr.richterhenry@gmail.com}} $|$
	\href{https://github.com/h3nryc0ding}{\underline{github.com/h3nryc0ding}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Diploma in Computer Science}{October 2021 -- September 2026}
{Dresden University of Technology}{Dresden, Germany}
\resumeItemListStart
\resumeItem{Grade average: 1.5 (German grading, ~3.7–4.0 GPA)}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Associate Software Developer Intern - Kubernetes}{September 2024 -- March 2025}
{ServiceNow}{Dublin, Ireland}
\resumeItemListStart
\resumeItem{Kubernetes Distribution: Refactored Ansible deployment pipeline by extracting reusable components into shared collections/plugins and improving integration with the Configuration Management Database (CMDB), a system for tracking IT assets and configurations. Rewrote playbooks to replace shell/command tasks with public Ansible plugins for better reliability.}
\resumeItem{Infrastructure Bootstrapping: Deployed core components via Flux using Helm charts, including Node/GPU Feature Discovery (NFD/GFD) and Trivy for misconfiguration/security scanning.}
\resumeItem{DevOps \& Testing: Optimized GitLab Kubernetes integration test pipeline, reducing runtime by 30\% and improving test accuracy. Created debug images for internal Docker builds to simplify troubleshooting.}
\resumeItem{Internal Tooling: Developed a Go authentication package for CMDB, using Cobra for CLI functionality and integrating with Keychain, 1Password, and an in-house secret store for secure credential management.}
\resumeItemListEnd

\resumeSubheading
{Full-Stack Developer Working Student – Web Applications}{October 2022 -- October 2024}
{Uniwunder}{Dresden, Germany}
\resumeItemListStart
\resumeItem{Frontend: Migrated from Angular 14 to 16 and refactored architecture to support Ionic, enabling cross-platform deployment (iOS/Android). Improved performance with lazy-loaded routing. Built a multi-step user form with dynamic validation and seamless backend integration.}
\resumeItem{Backend: Upgraded the existing Spring Boot backend from version 2 to 3. Added endpoints to support the multi-step form, handling complex user input and session state. Integrated Firebase Cloud Messaging for targeted push notifications.}
\resumeItem{DevOps: Created build pipelines for Android and iOS. Set up a self-hosted macOS runner to enable iOS builds.}
\resumeItemListEnd

\resumeSubheading
{IT Support Working Student – First-Level Support}{June 2021 -- September 2022}
{Jungheinrich}{Wilsdruff, Germany}
% \resumeItemListStart
% \resumeItem{Provided on-site setup and support for both hardware and software, ensuring optimal system performance.}
% \resumeItem{Configured and set up workplace environments to facilitate efficient workflows.}
% \resumeItem{Created and maintained MS Excel macros to automate tasks and improve productivity.}
% \resumeItem{Utilized tools such as a custom ticketing system and MS Active Directory for effective issue tracking and user management.}
% \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Kubernetes Deployment} $|$ \emph{Oracle Cloud, Kubernetes, Talos, Flux, Helm, GitOps}}{}
\resumeItemListStart
\resumeItem{Deployed a secure 3-node Kubernetes cluster on Oracle Cloud using Talos Linux, following GitOps practices with Flux CD and secret management via SOPS with Age.}
\resumeItem{Provisioned a production-grade infrastructure stack with Cilium CNI, OpenEBS for persistent storage, and database operators including CloudNativePG and MongoDB.}
\resumeItem{Automated ingress, DNS, and TLS with NGINX Ingress Controller, ExternalDNS, and Cert-Manager.}\resumeItemListEnd

\resumeProjectHeading
{\textbf{Livechat WebApp} $|$ \emph{Spring Boot, SvelteKit, MongoDB, Docker, Helm}}{}
\resumeItemListStart
\resumeItem{Built a live chat web application using Spring Boot and SvelteKit.}
\resumeItem{Implemented real-time messaging via WebSockets and integrated MongoDB for data persistence.}
\resumeItem{Developed a GraphQL API using Netflix DGS and secured the application with Spring Security and OAuth2.}
\resumeItem{Containerized the application and created a Helm chart as a proof of concept for Kubernetes deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages:}{ Kotlin, Java, Go, Python, TypeScript, C++, SQL, HTML/CSS} \\
		\textbf{Frameworks:}{ Spring Boot, Angular, SvelteKit} \\
		\textbf{Infrastructure:}{ Kubernetes, Docker, Helm, Flux, Ansible} \\
		\textbf{Developer Tools:}{ Git, GitHub/GitLab/Bitbucket CI/CD} \\
	}}
\end{itemize}

%-------------------------------------------
\end{document}
